Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-01-29 Thesis/chapter/061-results-emma.tex
finsih res-emma add lin-reg functions

\td{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{rational behind including $v_{cal}$ and $\lambda$ as optimisands}
The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ 
were included as dependent variables with the objective to maximize with a relative weight of 0.05 each.
The idea was to maximize $v_{cal}$ and minimize $\lambda$ in order to minimize the process time. 
Another thought behind including $v_{cal}$ and $\lambda$ was to test if the algorithm would correctly predict those. 
}
%
%Three major flaws behind this consideration became obvious with time: 
%
\
\ds{
(1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ (\oc{}/\h{} instead of \oc{}/\minutes{}) and $\lambda$, respectively. 
The algorithm will tend to include those values into the prediction function for 
all dependent variables and possibly exclude others which have more influence 
on $\gamma$ and $\rho$ (see equations (\ref{eq:emma-G4})? and (\ref{eq:emma-phd4})?).
%
(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
%
(3) needlessly making the problem more complicate %, important time (around 10\% of the samples) could have been replaced with more insightful samples. 
\begin{itemize}
    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
heating rate was one of the dependent variables with the intention of minimizing the variable. 
It can also be used as test to see how well the EMMA performs (or rather, more precisely MARS).
Even if it didn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
Overall there were too many variables involved for such a small dataset
        that means that adding dependent variables influences \td{previous variables}
\end{itemize}
}
%\td{look at emma papers}
%\td{change G to gamma and write enr to every figure}

%\td{in \cite{friedman1991multivariate} the model is said to work well on $\frac{N}{n}$ ratios (aka events per predictor varibale (EPV)) of 20-50. 
%EPV is around 5 for this model.
%Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
%"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%\subsubsection{how did evolve over time?}

\iffalse
\begin{figure}
\centering
\includegraphics[width=.6\textwidth]{Pics/stats/G-t.png}
    \caption{conductivity G [a.u.] against sample number (is this even correct?)}
    \label{fig:G-t}
\end{figure}

\td{TODO: check if the sorted correctly? Make generation graph with boxplot }
\td{TODO: visualize} how the population moved across the space (with parallel coordinates? or see page 121)
\url{https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation}
\fi
\td{TODO: find expression for $\gamma$: conductance measure, conducticity}

>>>>

\td{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%\subsubsection{how did evolve over time?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{rational behind including $v_{cal}$ and $\lambda$ as optimisands}
}
%
%Three major flaws behind this consideration became obvious with time: 
%
\
\td{
(1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ (\oc{}/\h{} instead of \oc{}/\minutes{}) and $\lambda$, respectively. 
The algorithm will tend to include those values into the prediction function for 
all dependent variables and possibly exclude others which have more influence 
on $\gamma$ and $\rho$ (see equations (\ref{eq:emma-G4})? and (\ref{eq:emma-phd4})?).
%
(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
%
(3) needlessly making the problem more complicate %, important time (around 10\% of the samples) could have been replaced with more insightful samples. 
\begin{itemize}
    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
heating rate was one of the dependent variables with the intention of minimizing the variable. 
It can also be used as test to see how well the EMMA performs (or rather, more precisely MARS).
Even if it didn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
Overall there were too many variables involved for such a small dataset
        that means that adding dependent variables influences \td{previous variables}
\end{itemize}
}

Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
%"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
%}

\td{TODO: find expression for $\gamma$: conductance measure, conducticity}
\td{when adding dep var to model this has two folgen: - beeinflusst the BF and the optimization, but bcs relatiev weight is only 0.05 for each, no big beeinflussung on optimization}

### 2023-01-29 Thesis/chapter/062-post-emma.tex
finsih res-emma add lin-reg functions

\label{sec:res-post-emma}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{ANOVA}\label{sec:res-anova}
\textbf{EMMA}
The \gls{rf} produced by the last iteration of \gls{emma} put a high \td{significance} 
on the calcination temperature $T_{cal}$ with regard to the \td{measurables} of the conductance. 
\Gls{anova} is used to double check this. 
%Now \gls{anova} can be used to check if the data

\textbf{What can/did we test?}
With \gls{anova} we can check if the probability of arriving at these results was by pure chance or not. 
The null hypothesis is that the results were obtained by pure chance without any dependence of the insulation of a sample on the process variables.
%We tested for each input variable the influence on rho and gamma 
A one-way \gls{anova} was performed for every independent variable on $\rho$ and $\gamma$. 
%and also as a test on vcal and $\lambda$. 
We used an $\alpha$ value of 0.05 which means that 
the null hypothesis is rejected if the p-value is under 0.05. 
Usually, the $\alpha$-value is chosen to be 0.01 or 0.05\cite{hoffman2020concept,sellke2001pvalues}.
The choice of a relatively high alpha-value is motivated by the rather small amount of data and low \td{EPV}.
As mentioned by Sellke et al.\cite{sellke2001pvalues} a p-value of 0.05 might tempt 
to guess that in 1 out of 20 cases the results could be false positives, 
whereas the frequency is much higher. 
%1 out of 20 times this result could be 
%produced by pure chance given that the null hypothesis is true. 
%If the p-value is below that value, then we choose to accept, that the data is not due to
%chance but due to the influence of the independent variables on the dependent variables. 
\td{could test anova on difference generation data sets}

@@

@@

>>>>

\label{sec:res-post-emma}
%describe what awaits the reader in this chapter:
In this section the experimental results are analyzed with different methods and compared with the original method EMMA which was integrated into the experiment selection process. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{ANOVA}\label{sec:res-anova}
%\textbf{EMMA}
The \gls{rf} produced by the last iteration of \gls{emma} put a high \td{significance/effect/correlation} 
on the calcination temperature $T_{cal}$ with regard to the \td{measurables} of the conductance. 
\Gls{anova} is used to double check this. 
%Now \gls{anova} can be used to check if the data

\textbf{What can/did we test?}
With \gls{anova} we can check if the probability of arriving at these results was by pure chance or not. 
The null hypothesis is that the results were obtained by pure chance without any dependence of the insulation of a sample on the process variables.
%We tested for each input variable the influence on rho and gamma 
A one-way \gls{anova} was performed for every independent variable on $\rho$ and $\gamma$. 
%and also as a test on vcal and $\lambda$. 
We used an $\alpha$ value of 0.05 which means that 
the null hypothesis is rejected if the p-value is under 0.05. 
Usually, the $\alpha$-value is chosen to be 0.01 or 0.05\cite{hoffman2020concept,sellke2001pvalues}.
The choice of a relatively high alpha-value is motivated by the rather small amount of data and low \td{EPV}.
As mentioned by Sellke et al.\cite{sellke2001pvalues} a p-value of 0.05 might tempt 
to guess that in 1 out of 20 cases the results could be false positives, 
whereas the frequency is much higher. 
%1 out of 20 times this result could be 
%produced by pure chance given that the null hypothesis is true. 
%If the p-value is below that value, then we choose to accept, that the data is not due to
%chance but due to the influence of the independent variables on the dependent variables. 
\td{could test anova on different generations data sets}

@@

\begin{align}
	\begin{split}
		\label{eq:linreg-phd}
		\hat{\rho} =&  -0.022\cdot c_{zr} -0.022\cdot \lambda -0.0029\cdot v_{DB} + 0.0058\cdot T_{DB} \\
		& -8.5\cdot 10^{-5}\cdot v_{cal} + 0.0026\cdot T_{cal} -0.76
	\end{split}
	\\
	\begin{split}
		\label{eq:linreg-G}
		\hat{\gamma} ={} & 3.2\cdot c_{zr} - 0.97\cdot \lambda - 1.2\cdot v_{DB} + 0.2\cdot T_{DB} \\
			& - 0.014\cdot v_{cal} + 0.13\cdot T_{cal} + 7.2
	\end{split}
\end{align}

@@

\td{do regression for avg(-log(G)) instead of $\gamma$=avg( ( 13+log(G))**2)}
